### 2018-01-15 manuscript.rmd
updated subsample script

Euphysonectae consists of two reciprocally monophyletic groups we here provisionally refer to as Clade A and Clade B (Fig. 3A). Clade A is a group of siphonophores that all have an involucrum, or fold, that forms around the base of the cnidoband [@totton1965synopsis]. This clade also shares the prescence of a descending mantle canal within the nectophores (Fig. S6), and is also monoecious (Fig. 5). Within Clade B there is low support for the placement of *Erenna richardi*, which is placed as sister to Clade A in some analyses (Fig. 3B). More taxon sampling will be required to determine the relationship of species within this clade.

@@

Using the Swofford-Olsen-Waddell-Hillis (SOWH) test [@swofford1996phylogenetic], we evaluated the following three alternative phylogenetic hypotheses against the most likely tree topology (Fig. 3C): (i) monophyletic Physonectae, (ii) monophyletic monoecious siphonophores (both with and without *Rudjakovia* sp.). In all three tests the alternative hypothesis was rejected (p-value <0.01, confidence interval: <0.001 - 0.03, Fig. S2).

@@

In all siphonophores, each gonophore (sexual medusa that produces gametes) is either male or female. Within each siphonophore species, colonies are either monoecious (male and female gonophores are on the same colony) or dioecious (male and female gonophores are on different colonies). Previous analyses suggested that the common ancestor of siphonophores was dioecious, and was consistent with a single gain of monoecy within the Codonophora and no secondary losses [@Dunn:2005dy]. The better-resolved tree in the current analyses indicates that the evolution of monoecy is more complicated than this. The two clades of monophyloetic siphonophores, Calycophorae and Clade A (Fig. 3A), do not form a monophyletic group. This is because Clade B, which contains dioecious species, is also desceneded from their most recent common ancestor. SOWH tests strongly reject the placement of the monecious clades Calycophorae and Clade A as a group that excludes Clade B (Figs. 3C and S2). The positions of the only two taxa from Clade B in the previous analysies [@Dunn:2005dy], *Erenna* and *Stephalia*, were unresolved in that previous study. This difference in conclusions regarding trait evolution therefore does not reflect a contradication between alternative strongly supported results, but the resolution of earlier polytomies in a way that indicates there has been homoplasy in the evolution of monoecy.

>>>>

Euphysonectae consists of two reciprocally monophyletic groups that we here provisionally refer to as Clade A and Clade B (Fig. 3A). Clade A is a group of siphonophores that all have an involucrum, or fold, that forms around the base of the cnidoband [@totton1965synopsis]. This clade also shares the prescence of a descending mantle canal within the nectophores (Fig. S6), and is also monoecious (Fig. 5). Within Clade B there is low support for the placement of *Erenna richardi*, which is placed as sister to Clade A in some analyses (Fig. 3B). More taxon sampling will be required to determine the relationship of species within this clade.

@@

Using the Swofford-Olsen-Waddell-Hillis (SOWH) test [@swofford1996phylogenetic], we evaluated the following three alternative phylogenetic hypotheses against the most likely tree topology (Fig. 3C): (i) monophyletic Physonectae, (ii) and (iii) monophyletic monoecious siphonophores,with and without *Rudjakovia* sp. respectively. In all three tests the alternative hypothesis was rejected (p-value <0.01, confidence interval: <0.001 - 0.03, Fig. S2).

@@

In all siphonophores, each gonophore (sexual medusa that produces gametes) is either male or female. Within each siphonophore species, colonies are either monoecious (male and female gonophores are on the same colony) or dioecious (male and female gonophores are on different colonies). Previous analyses suggested that the common ancestor of siphonophores was dioecious, and was consistent with a single gain of monoecy within the Codonophora and no secondary losses [@Dunn:2005dy]. The better-resolved tree in the current analyses indicates that the evolution of monoecy is more complicated than this. The two clades of monophyloetic siphonophores, Calycophorae and Clade A (Fig. 3A), do not form a monophyletic group. This is because Clade B, which contains dioecious species, is also desceneded from their most recent common ancestor. SOWH tests strongly reject the placement of the monecious clades Calycophorae and Clade A as a group that excludes Clade B (Figs. 3C and S2). The positions of the only two taxa from Clade B in the previous analysies [@Dunn:2005dy], *Erenna* and *Stephalia*, were unresolved in that previous study. This difference in conclusions regarding trait evolution, therefore, does not reflect a contradication between alternative strongly supported results, but the resolution of earlier polytomies in a way that indicates there has been homoplasy in the evolution of monoecy.
